---
title: "MGIS.FW_Units"
format: html
editor: visual
---

# 0.0 Environment Set-up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Loads libraries from LPDB_libraries.R script
source("C:/Project_Work/parcels-processing/PDB_Update_2023/LPDB_libraries.R")

# Load functions from LPDB_functions.R script
source("C:/Project_Work/parcels-processing/PDB_Update_2023/LPDB_functions.R")

#
keys <- mapcdatakeys::all_muni_data_keys |> 
  select(c(muni_id, cmtyp08, rpa_acr))

#Global options to remove scientific notation.
options(scipen = 999)
set.seed(351)

#Set root variables for local data ingestion
local_root <- "C:/Project_Work/Local_Data/Parcel_DB/"

#Set root variable for network data ingestion
network_root <- "K:/DataServices/Datasets/Parcel_DB/Data/LPDB_Update_Dec.23_Jan.24/parcels_by_muni/"
```

# 1.0 Loading in Data
# 1.1 Loading in Geodatabase with Parcel data
```{r}
# Check which layers exist in the geodatabase
layers <- st_layers(dsn = "C:/Project_Work/Local_Data/Parcel_DB/Q1_2026/MassGIS_L3_Parcels.gdb")
print(layers$name)

# Read in the assessors records from the geodatabase
assessors <- st_read(dsn = "C:/Project_Work/Local_Data/Parcel_DB/Q1_2026/MassGIS_L3_Parcels.gdb", layer = layers$name[3])

# Read in the MassGIS Land Use Code Crosswalk
use_codes <- st_read(dsn = "C:/Project_Work/Local_Data/Parcel_DB/Q1_2026/MassGIS_L3_Parcels.gdb", layer = layers$name[2]) |> 
  left_join(keys, by = c("TOWN_ID" = "muni_id"))

print(sapply(X = assessors, FUN =  function(x) sum(is.na(x))))

print(summary(assessors))

print(str(assessors))

```

# 1.2 Load Complementary Datasets
```{r}
# Load CAMA System and Maintainer file from MassGIS
# File download from 1/19/2026
cama <- read.csv(paste0(local_root, "/Complementary Data/Municipal_Parcel_Status_for_Dashboard_(Feature_Service)_Layer.csv"))
  
# Load the Municipality x Neighborhood Crosswalk
nbhd_xwalk <- mapcdatakeys::nbhd_muni_xw

# Loads the land use codes crosswalk
USE_CODE_XWALK <- readRDS("C:/Project_Work/Local_Data/Parcel_DB/Land.Use.Code_Crosswalks/muni.use_code_xwalk.2026.02.rds") |>
  #Replace all N/A Variables with "Unknown"
  mutate(across(everything(), ~replace_na(.x, "Unknown"))) |> 
  distinct(MUNI.USE_CODE, .keep_all = TRUE) |> 
  select(-c(muni_name))

```

# 1.3 Load Municipal and State-wide Comparison Datasets
```{r}
# Verified Unit Count Data
# Watertown
# watertown_vu <-
# Camrbridge
cambridge_vu <- read.csv("C:/Project_Work/Local_Data/Parcel_DB/MassGIS Framework Grant/External Data/Unit Count/Land_Use_Data_2025_20260423_Cambridge.csv") 

# Somerville
somerville_vu <- read_xlsx(
  path = "C:/Project_Work/Local_Data/Parcel_DB/MassGIS Framework Grant/External Data/Unit Count/Somerville Assessor Data (FY2026) 04-21-2026.xlsx",
  sheet = 1)

# Boston

# Estimated Unit Count Data from Massachusetts Housing Partnership (Residensity Project)

# Census Master Address File Aggregations.


```

# 1.4 Load Parcel and Structure Supplementary Data
```{r}
# Building Heights
```

# 2.0 Current Conditions Analysis
# 2.1 Clean assessors table
```{r}
# Clean assessors data to do an analyze residential parcel data for missing or zero unit counts.
assessors_cleaned <- assessors |> 
  left_join(
    USE_CODE_XWALK,
    by = c("USE_CODE" = "MUNI.USE_CODE")
  ) |>
  mutate(
    # Create filter for residential land uses based on the Standard Land Use code.
    filter_flag = str_sub(STD.USE_CODE, start = 1, end = 1),
    # Coerce CITY to title case to join to neighborhood crosswalk.
    CITY = stringr::str_to_title(CITY),
    # Replace NAs in "UNIT" variable
    UNITS = replace_na(UNITS, 999)
  ) |>
  # Join the Neighborhood Crosswalk to clean Assessor's table "CITY" variable names.
  left_join(
    nbhd_xwalk,
    by = c("CITY" = "neighborhood")
  ) |> 
  # Join mapcdatakeys for community type and RPA variables. 
  left_join(
    keys,
    by = c("muni_id")
  ) |>
  # Join MassGIS CAMA Systems dataframe for CAMA System and parcel maintainer information.
  left_join(
    cama,
    by = c("muni_id" = "TOWN_ID")
  )

```

# 2.2 Summarize Missing Data or Zeroes in "UNITS" Variable
```{r}
# Subset of all residential parcels.
res_sub.all_units <- assessors
# Filter for Residential Uses Only
  filter(filter_flag == "1") |> 
  distinct(LOC_ID, .keep_all = TRUE)

# Subset of all residential parcels with NA or zero units.
res_sub.no_units <- assessors
  filter(filter_flag == "1" & (UNITS == 999 | UNITS == 0)) |> 
  distinct(LOC_ID, .keep_all = TRUE)
  
# 1. Number Parcels with X number of units
Num_units <- assessors_subset |> 
  group_by(UNITS) |> 
  summarise(
    num_parcels = n()
  ) |> 
  ungroup()

# 2. Number Parcels with X number of units and Municpality
Num_units.city <- assessors_subset |> 
  group_by(UNITS, muni_name) |> 
  summarise(
    num_parcels = n()
  ) |> 
  ungroup() |> 
  group_by(muni_name) |> 
  mutate(
    tot_parcel = sum(num_parcels)
  ) |> 
  ungroup() |> 
  arrange(desc(tot_parcel))

# 3. Number Parcels with X number of units and Community Type
Num_units.cmtyp<- assessors_subset |> 
  group_by(UNITS, cmtyp08) |> 
  summarise(
    num_parcels = n()
  ) |> 
  ungroup() |> 
  group_by(cmtyp08) |> 
  mutate(
    tot_parcel = sum(num_parcels)
  ) |> 
  ungroup() |> 
  arrange(desc(tot_parcel))

# 4. Number Parcels with X number of units and RPA
Num_units.rpa <- assessors_subset |> 
  group_by(UNITS, rpa_acr) |> 
  summarise(
    num_parcels = n()
  ) |> 
  ungroup() |> 
  group_by(rpa_acr) |> 
  mutate(
    tot_parcel = sum(num_parcels)
  ) |> 
  ungroup() |> 
  arrange(desc(tot_parcel))

# 5. Number Parcels with X number of units and CAMA
Num_units.cama <- assessors_subset |> 
  group_by(UNITS, CAMA_SYS) |> 
  summarise(
    num_parcels = n()
  ) |> 
  ungroup() |> 
  group_by(CAMA_SYS) |> 
  mutate(
    tot_parcel = sum(num_parcels)
  ) |> 
  ungroup() |> 
  arrange(desc(tot_parcel))

# 6. Number Parcels with X number of units and Parcel Maintainer
Num_units.pm <- assessors_subset |> 
  group_by(UNITS, PAR_MAINT_BY) |> 
  summarise(
    num_parcels = n()
  ) |> 
  ungroup() |> 
  group_by(PAR_MAINT_BY) |> 
  mutate(
    tot_parcel = sum(num_parcels)
  ) |> 
  ungroup() |> 
  arrange(desc(tot_parcel))

# 7. Number Parcels with X number of units and Residential Land Use Code
Num_units.LUCA <- assessors_subset |> 
  group_by(UNITS, STD.USE_CODE) |> 
  summarise(
    num_parcels = n()
  ) |> 
  ungroup() |> 
  group_by(STD.USE_CODE) |> 
  mutate(
    tot_parcel = sum(num_parcels)
  ) |> 
  ungroup() |> 
  arrange(desc(tot_parcel))

```

# 2.3 Checking Validity of Verification of Municipal Unit Counts
```{r}
# 
# Watertown

# Cambridge
ac_cambridge <- assessors_cleaned |> 
  filter(muni_name == "Cambridge")
# Somerville
ac_somerville <- assessors_cleaned |> 
  filter(muni_name == "Somerville")

# Boston

# 
```

# 2.4 Comparison of Assessor's Table "UNIT" Counts to Census Master Address File Aggregations
```{r}
```

# 2.5 Comparison of Assessor's Table "UNIT" Counts to MHP "Residensity" Product
```{r}
```

# 2.6 Comparison of Assessor's Table "UNIT" Counts to MAPC "Land Parcel Database" Product
```{r}
```

# 2.7 Compare MHP "Residensity" Product to  MAPC "Land Parcel Database" Product
```{r}
```

# 3.0

# 4.0 Estimation of Parcel Level Unit Count Data
# 4.1 Join Relevant Data to Assessor's Table
```{r}
```

# 4.2 Create Testing and Training Datasets from Verified Unit Count Municipalities
```{r}
```
