---
title: "MGIS.FW_LandUseCodes"
format: html
editor: visual
---

# 0.0 Environment Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load "here" library
library(here)

# Loads libraries from LPDB_libraries.R script
source(here("03_Scripts/LPDB_libraries.R"))

# Load functions from LPDB_functions.R script
source(here("03_Scripts/LPDB_functions.R"))

# Load data keys to crosswalk municipality names to municipal IDs
keys <- mapcdatakeys::all_muni_data_keys |> 
  select(c(muni_name,muni_id)) |> 
  mutate(muni_name = stringr::str_to_title(muni_name))

# Set list of stopwords
# Create different case variations of stop words
sw.upper <- str_to_upper(stopwords(source = "snowball"))
sw.title <- str_to_title(stopwords(source = "snowball"))
sw.lower <- str_to_lower(stopwords(source = "snowball"))

# Create single list of case variant stop words
sw <- c(sw.upper, sw.title, sw.lower)
# Remove intermediate stop word lists
rm(sw.upper, sw.title, sw.lower)

#Global options to remove scientific notation and set random seed
options(scipen = 999)
set.seed(351)

# Set Land Use Code Vintage
q <- "Q1"
y <- "2026"
```

# 1.0 Loading in Data
# 1.1 Loading in Geodatabase with Parcel data and filtering for attributes

```{r}
# Check which layers exist in the geodatabase
layers <- st_layers(dsn = here("02_Data/Raw/MGIS Property Tax Parcels/MGIS Q1 2026/MassGIS_L3_Parcels.gdb"))
print(layers$name)

# Read in the assessors records from the geodatabase
assessors <- st_read(dsn = here("02_Data/Raw/MGIS Property Tax Parcels/MGIS Q1 2026/MassGIS_L3_Parcels.gdb"), layer = layers$name[3])

# Read in the MassGIS Land Use Code Crosswalk
use_codes <- st_read(dsn = here("02_Data/Raw/MGIS Property Tax Parcels/MGIS Q1 2026/MassGIS_L3_Parcels.gdb"), layer = layers$name[2]) |> left_join(keys, by = c("TOWN_ID" = "muni_id"))

print(sapply(X = use_codes, FUN =  function(x) sum(is.na(x))))

print(summary(use_codes))

print(str(use_codes))
```

# 1.2 Load Complementary Datasets

```{r}
# Load CAMA System and Maintainer file from MassGIS
# File download from 1/19/2026
cama <- read.csv(here("02_Data/Raw/Land Use Codes/Municipal_Parcel_Status_for_Dashboard_(Feature_Service)_Layer.csv"))

# Load MAPC Data Keys for municipalities
full.keys <- mapcdatakeys::all_muni_data_keys |> select(muni_id, rpa_acr, cmtyp08)

```

# 2.0 Cleaning MassGIS Land-Use Code File
# 2.1 Create a standard land use code data frame

```{r}
# Check Use Code Crosswalk data types
str(use_codes)

# Create a dataframe of the L3 standardized use codes.
std_uc <- use_codes |> 
  # TOWN_ID is 0 for the L3 Use Codes
  filter(TOWN_ID == 0) |> 
  # Create
  mutate(
    od_uc = str_sub(USE_CODE, start = 1, end = 1),
    td_uc = str_sub(USE_CODE, start = 1, end = 2),
    xwalk_uc = str_sub(USE_CODE, start = 1, end = 3)
  ) |> 
  # Create a distinct name for the Use Code and Use Code Description to denote the standard code
  dplyr::rename(
    STD.USE_CODE = USE_CODE,
    STD.USE_DESC = USE_DESC
  ) |> 
  # Remove superfluous variables
  select(-c(muni_name, TOWN_ID))

# QC Checks for standard use code 
# Check the number of unique 1-, 2-, and 3-digit land-use codes
print(length(unique(std_uc$od_uc))) # Should be equal to 10 (0-9)
print(length(unique(std_uc$td_uc))) # Should be equal to 54
print(length(unique(std_uc$xwalk_uc))) # Should be equal to 304 (296 + deprecated 901-908 codes)

# Create a list of standard use codes MassGIS details in the LUT file with a Town ID of "0"
std_uc_list <- std_uc |> select(STD.USE_CODE) |> pull()

# Two-digit Use Codes not in the codebook
# 00 - Unknown use
# 04 - Primarily industrial mixed use
# 06 - Primarily forest mixed use
# 07 - Primarily agriculture mixed use
# 08 - Primarily recreation mixed use
# 29 - Not technically a specific two-digit category but is included in the unproductive land category.

# Three-digit Use Codes not in the codebook
# 0 - Mixed Use (35)
#   000 - Unknown Use or use code not provided
#   014 - Primarily Residential, some industrial 
#   016 - Primarily Residential, some forest
#   017 - Primarily Residential, some agriculture
#   018 - Primarily Residential, some recreation
#   019 - Primarily Residential, some tax exempt
#   030 - Primarily Commercial, some other
#   034 - Primarily Commercial, some industrial
#   036 - Primarily Commercial, some forest
#   038 - Primarily Commercial, some recreation
#   040 - Primarily Industrial, some other
#   041 - Primarily Industrial, some residential
#   043 - Primarily Industrial, some commercial
#   046 - Primarily Industrial, some forest
#   047 - Primarily Industrial, some agriculture
#   048 - Primarily Industrial, some recreation
#   061 - Primarily Forest, some residential
#   063 - Primarily Forest, some commercial
#   064 - Primarily Forest, some industrial
#   067 - Primarily Forest, some agriculture
#   068 - Primarily Forest, some recreation
#   071 - Primarily Agriculture, some residential
#   073 - Primarily Agriculture, some commercial
#   074 - Primarily Agriculture, some industrial
#   076 - Primarily Agriculture, some forest
#   078 - Primarily Agriculture, some recreation
#   081 - Primarily Recreation, some residential
#   083 - Primarily Recreation, some commercial
#   084 - Primarily Recreation, some industrial
#   086 - Primarily Recreation, some forest
#   087 - Primarily Recreation, some agriculture
# 1 - Residential (19)
# 2 - Open Space (31)
# 3 - Commercial (72)
# 4 - Industrial (29)
#   422 - Electrical Plant
# 5 - Personal Property (10)
# 6 - Chapter 61 Property (2)
# 7 - Chapter 61 Property (11)
# 8 - Chapter 61 Property (15)
# 9 - Tax Exempt (72)
```

# 2.2 Create a dataframe of municipal specific land use codes
```{r}
# List of strings common to undefined Mixed Use use codes which indicate whether or not they are ACTUALLY Mixed Use, as opposed to misclassified single use.
# Primary Mixed Use Strings
mu.strings <- c("Mixed", "mixed", "MIXED", "mixedj", "mix", "Mix", "MIX", "MXD", "mxd", "MU ", "Mu ", "mu ", "primary", "Primary", "primarily", "Primarily","PR ", "Pr ", "pr ",  "PRI ", "pri ", "Pri ", "PRI- ", "pri- ", "Pri- ", "-use", "-Use", "-USE", " use", " USE", " Use", "predom", "Predom", "PREDOM")

# Secondary Mixed Use terms/indicators
td.mu.strings <- c("//,", "///", " and", " AND", " And", " with", " With", " WITH", " on", " On", " ON")

# Create Municipal Use Code dataframe
muni_uc <- use_codes |> 
  filter(TOWN_ID != 0) |> 
  mutate(
    # Clean whitespace out of the Muni Use Codes
    USE_CODE = str_trim(USE_CODE, "both"),
    # Create three-digit x_walk
    xwalk_uc = str_sub(USE_CODE, start = 1, end = 3),
    # Mixed Use Flag
    mu.flag = str_detect(USE_DESC, paste(mu.strings, collapse = "|")),
    # Flag for a leading zero
    lead_z = str_starts(USE_CODE, "0"),
    # Flag for a trailing zero
    trail_z = str_ends(USE_CODE, "0"),
    # Counts the number of digits in each use code.
    digits = str_length(USE_CODE),
    # Boolean for presence of contextual extension
    letters = str_detect(USE_CODE, "[:alpha:]")
  )|> 
  dplyr::rename(
    MUNI.USE_CODE = USE_CODE,
    MUNI.USE_DESC = USE_DESC
  ) |>  
  # Join Data Keys dataframe
  left_join(full.keys, by = c("TOWN_ID" = "muni_id")) |> 
  # Join CAMA Data frame from MassGIS
  left_join(cama, by = c("TOWN_ID"))

# Create Dataframe of Non-standard use codes from the muni list
non_std <- muni_uc |> filter(!MUNI.USE_CODE %in% std_uc_list)

print(nrow(non_std)/nrow(muni_uc))

```

# 3.0 Municipal Land Use Codes Analysis and QC
# 3.1 With Mixed Use Codes
```{r}
# Filter out Leading and Trailing Zeros
nonstd_w.mu_wo.ltz <- non_std |> 
  filter(lead_z == FALSE & trail_z == FALSE)

# Number of digits
tbl.1_digits <- nonstd_w.mu_wo.ltz |> 
  group_by(digits) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Municipality
tbl.1_muni <- nonstd_w.mu_wo.ltz |> 
  group_by(muni_name) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  ) 

# RPA
tbl.1_rpa <- nonstd_w.mu_wo.ltz |> 
  group_by(rpa_acr) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Community Type
tbl.1_cmtyp08 <- nonstd_w.mu_wo.ltz |> 
  group_by(cmtyp08) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# CAMA System
tbl.1_cama <- nonstd_w.mu_wo.ltz |> 
  group_by(CAMA_SYS) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Maintainer
tbl.1_maint <- nonstd_w.mu_wo.ltz |> 
  group_by(PAR_MAINT_BY) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Contextualizing Non-numerics
tbl.1_letters <- nonstd_w.mu_wo.ltz |> 
  group_by(letters) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# No filter for leading and trailing zeros
nonstd_w.mu_w.ltz <- non_std

# Number of digits
tbl.2_digits <- nonstd_w.mu_w.ltz |> 
  group_by(digits) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Municipality
tbl.2_muni <- nonstd_w.mu_w.ltz |> 
  group_by(muni_name) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  ) 

# RPA
tbl.2_rpa <- nonstd_w.mu_w.ltz |> 
  group_by(rpa_acr) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Community Type
tbl.2_cmtyp08 <- nonstd_w.mu_w.ltz|> 
  group_by(cmtyp08) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# CAMA System
tbl.2_cama <- nonstd_w.mu_w.ltz |> 
  group_by(CAMA_SYS) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Maintainer
tbl.2_maint <- nonstd_w.mu_w.ltz |> 
  group_by(PAR_MAINT_BY) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Contextualizing Non-numerics
tbl.2_letters <- nonstd_w.mu_w.ltz |> 
  group_by(letters) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

```

# 3.2 Without Mixed Use Codes

```{r}
# Filter out Leading and Trailing Zeros
nonstd_wo.mu_wo.ltz <- non_std |> 
  filter(mu.flag == FALSE & lead_z == FALSE & trail_z == FALSE)

# Number of digits
tbl.3_digits <- nonstd_wo.mu_wo.ltz |> 
  group_by(digits) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Municipality
tbl.3_muni <- nonstd_wo.mu_wo.ltz |> 
  group_by(muni_name) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  ) 

# RPA
tbl.3_rpa <- nonstd_wo.mu_wo.ltz |> 
  group_by(rpa_acr) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Community Type
tbl.3_cmtyp08 <- nonstd_wo.mu_wo.ltz|> 
  group_by(cmtyp08) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# CAMA System
tbl.3_cama <- nonstd_wo.mu_wo.ltz |> 
  group_by(CAMA_SYS) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Maintainer
tbl.3_maint <- nonstd_wo.mu_wo.ltz |> 
  group_by(PAR_MAINT_BY) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Contextualizing Non-numerics
tbl.3_letters <- nonstd_wo.mu_wo.ltz |> 
  group_by(letters) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# No filter for leading and trailing zeros
nonstd_wo.mu_w.ltz <- non_std |> 
  filter(mu.flag == FALSE)

# Number of digits
tbl.4_digits <- nonstd_wo.mu_w.ltz |> 
  group_by(digits) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Municipality
tbl.4_muni <- nonstd_wo.mu_w.ltz |> 
  group_by(muni_name) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  ) 

# RPA
tbl.4_rpa <- nonstd_wo.mu_w.ltz |> 
  group_by(rpa_acr) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Community Type
tbl.4_cmtyp08 <- nonstd_wo.mu_w.ltz|> 
  group_by(cmtyp08) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# CAMA System
tbl.4_cama <- nonstd_wo.mu_w.ltz |> 
  group_by(CAMA_SYS) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Maintainer
tbl.4_maint <- nonstd_wo.mu_w.ltz |> 
  group_by(PAR_MAINT_BY) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )

# Contextualizing Non-numerics
tbl.4_letters <- nonstd_wo.mu_w.ltz |> 
  group_by(letters) |> 
  summarise(
    tot_uc = n()
  ) |> 
  ungroup() |> 
  mutate(
    pct_uc = round(tot_uc/sum(tot_uc), 4)*100
  )
```

# 3.1 Sidebar - Analysis of Non-Standard Land Use Codes for LUZI Task One

```{r}
# Create a df of all non-standard use codes defined as all use codes NOT a standard use code as included in the MassGIS LUT file with a Town ID of "0"
# Join mapcdatakeys for community type and RPA variables. 
# Join MassGIS CAMA Systems dataframe for CAMA System and parcel maintainer information.
non_std <- muni_uc |>
  mutate(MUNI.USE_CODE = str_trim(MUNI.USE_CODE, "both")) |>
  filter(!MUNI.USE_CODE %in% test) |> 
  left_join(
    full.keys,
    by = c("TOWN_ID" = "muni_id")
  ) |> 
  left_join(
    cama,
    by = c("TOWN_ID")
  )

# Create summary tables.
# 
non_std.tbl <- non_std |>
  group_by(muni_name) |>
  summarise(
    use_codes_1 = n()
  ) |>
  ungroup()

# 
non_std.tbl_sansmu <- non_std |>
  mutate(
    mu.flag = str_detect(MUNI.USE_DESC, paste(mu.strings, collapse = "|")),
    lead_z = str_starts(MUNI.USE_CODE, "0"),
    trail_z = str_ends(MUNI.USE_CODE, "0")
  ) |>
  filter(mu.flag == FALSE & lead_z == FALSE & trail_z == FALSE) |>
  group_by(muni_name) |>
  summarise(
    use_codes_2 = n()
  ) |>
  ungroup()

# Table of total non-standard codes by RPA
non_std.rpa.tbl <- non_std |>
  group_by(rpa_acr) |>
  summarise(
    use_codes_1 = n(),
    muni = length(unique(TOWN_ID)),
  ) |>
  ungroup() |> 
  mutate(
    nsuc.per.muni = use_codes_1/muni
  )

# Table of total non-standard codes by Community Type
non_std.cmtyp.tbl <- non_std |>
  group_by(cmtyp08) |>
  summarise(
    use_codes_1 = n(),
    muni = length(unique(TOWN_ID)),
  ) |>
  ungroup() |> 
  mutate(
    nsuc.per.muni = use_codes_1/muni
  )

# Table of total non-standard codes by CAMA System
non_std.cama.tbl <- non_std |>
  group_by(CAMA_SYS) |>
  summarise(
    use_codes_1 = n(),
    muni = length(unique(TOWN_ID)),
  ) |>
  ungroup() |> 
  mutate(
    nsuc.per.muni = use_codes_1/muni
  )

# Table of total non-standard codes by Maintainer
non_std.main.tbl <- non_std |>
  group_by(PAR_MAINT_BY) |>
  summarise(
    use_codes_1 = n(),
    muni = length(unique(TOWN_ID)),
  ) |>
  ungroup() |> 
  mutate(
    nsuc.per.muni = use_codes_1/muni
  )

# 
tbl <- full_join(non_std.tbl, non_std.tbl_sansmu, by = c("muni_name")) |> mutate(use_codes_2 = replace_na(use_codes_2, 0))
#
write.csv(tbl, "C:/Project_Work/Local_Data/Parcel_DB/Data Request/non_std_use.code_muni_summary.csv", row.names = FALSE)
```
